% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{CPD Report}

% Please do not change the subtitle
\subtitle{COMP330}

% Please put your student number in the author field
\author{1607804}

\begin{document}

\maketitle
%abstract{Please include an abstract of at most 100 words (these do not count towards your word count).}

\section{Introduction}
My experience of freelance app development has put into perspective some of the challenges one faces when dealing with real-world deadlines. In addition, it allowed me to see the benefits of working for a larger company. The opportunity to learn from more experienced programmers and gain industry experience is worth more to me at this time than being a freelance developer. To this end, my main career goal is to find a place of employment at a software engineering company. Ideally, my employment would allow me to develop my skills in back-end web development and other distributed software engineering practices. For a long-term goal I would like to explore the possibilities of management, but before then I will need to gain industry experience. I believe finding employment in the games industry in Cornwall will prove to be more challenging than other industries. I would like to stay Cornwall for the next few years, as such, my career seems to be pointed away from the games industry.

\section{Affective Domain: The ability to control my frustration towards colleagues}
Game development requires many different areas of expertise, as such, it attracts people from all walks of life. When I transition into a workplace I may find people whom I do not see eye to eye. The ability to control my frustration when differences occur will stop any negative effects my emotions may have on my interpersonal relations. This semester, the different work ethic and schedules of my colleagues has caused me great frustration. My lack of control over this emotion may have caused some members of the team to feel isolated. Feeling this way may have made it harder for them to contribute, thus negatively impacting both the team and the game. \\
\textbf{S.}    I will download the app called Headspace and complete the ten-day basic course.\\
\textbf{M.}   Headspace has a basic ten-day course, this course is clearly segmented so I will measure my progress through the app.\\
\textbf{A.}   Having this course available for free and on my phone will give me access to it at any time with no expense to myself. \\
\textbf{R.}  Building a new habit of meditation into my life could reduce my overall stress. Moreover, this course teaches meditation techniques so when I start to become frustrated I can use these techniques to control my frustration.\\
\textbf{T.}  I will start the ten-day course on Monday 7th. Therefore, I will have completed the basic course before my lectures begin again.\\

\section{Interpersonal Domain: To be able to effectively lead a small team.}
 Within any industry, there is a need for individuals to lead teams. Managing roles can be recognised formally or, when colleagues of equal standing self appoint a leader, informally. An effective leader can increase productivity in addition to increasing interpersonal relations within a team. This semester I found myself taking on a pseudo-leader role with my colleagues coming to me for advice and guidance. My lack of confidence and knowledge on how to lead made my shy away from the role. As a result, my team did not always get the advice and guidance a more proficient leader could have provided.\\
\textbf{S.} I will complete the two beginner level tutorials on Lynda.com titled \href{https://www.lynda.com/course-tutorials/Managing-Teams-2018/746304-2.html}{``Managing teams''} and  \href{https://www.lynda.com/Leadership-Management-tutorials/Inspirational-leadership/756283/5006410-4.html}{``Leading with emotional intelligence''}. \\
\textbf{M.}  I will measure my progress by how much of the tutorials I have watched. \\
\textbf{A.}  Logging in through Falmouth University's' website allows access to these tutorials for me to watch whenever I have free time, the tutorials are roughly one hour each, although I may have to rewatch parts of interest.\\
\textbf{R.} The tutorials on Lynda.com are of the highest quality. Watching these two tutorials will help me learn techniques to manage team and do it with emotional intelligence. \\
\textbf{T.} I will make sure I watch both of the tutorials at least once before my first lecture of the new year. This way I can put what I have learned into practice becoming a more effective leader.\\

\section{Dispositional Domain: Managing my break times effectively}
The standard industry practice is to have at least one break a day. If one were to start to at 9am it is typical to take roughly a thirty-minute break anywhere between 12-2. This semester, I have found myself coming in at 9am, but not having any consistency when it came to taking a break. Some days I found myself working until 3pm before hunger would drive me away from the computer. Not taking these much-needed breaks has caused me some discomfort. When faced with a particularly challenging problem I have found it beneficial to take a break and come back with a fresh pair of eyes. \\
\textbf{S.} I will read and practice an advice article by \href{https://www.siliconrepublic.com/advice/work-breaks-stress-productivity}{Siliconrepublic}.\\
\textbf{M.} I will measure my progress by how often I stick to the advice provided by the article.\\
\textbf{A.} Taking breaks will be difficult when I am engaged with a challenging problem. However, I believe having a clear plan for my breaks will make it much easier to walk away from my work.\\
\textbf{R.} Having an aim and structure to my break will not only increase the effectiveness of the breaks but also will increase the consistency of when I take breaks. \\
\textbf{T.} I will make sure I get into the routine of taking regular effective breaks before the end of the academic year. 

\section{Cognitive Domain: To know a framework for lightweight native app development}
 Through speaking with local software engineering professionals I have learnt of the high demand for app development. The demand for cross-platform apps is far larger than the demand for games. The two frameworks I currently know Unity  and UE4  are not suitable for this kind of development. As a result, I had to turn down monetary offers for simple design requests. \\
\textbf{S.} I will complete one beginner and one intermediate Apache Cordova tutorial on Lynda.com .\\
\textbf{M.} I will measure my progress by how much of the tutorials I have watched and understand.\\
\textbf{A.} Once more, my access to Lynda.com has made this an easy target to achieve.\\
\textbf{R.} Apache Cordova allows developers to create native apps using HTML, CSS and Javascript, it is a lighter framework making it more suitable for the type of apps local businesses demand.\\
\textbf{T.} If I want to make apps for clients I will need to have a good understanding of Apache Cordova before I leave university. I will aim to complete this target before may of 2019.\\

\section{Procedural Domain: To utilise my C++ knowledge when working in UE4}
After multiple modules where I have had to use C++, I have a good understanding of the language.  However, when working in UE4 I find myself falling on blueprints to do a lot of tasks that can be done in C++. Using C++ instead of blueprints will increase performance as well as further improve my understanding of the language. The value of knowing blueprints is reduced to nothing when applying to companies that do not use UE4.\\
\textbf{S.} I will create the inventory system needed for our game using C++. \\
\textbf{M.} I will measure my progress by how functional and complete the inventory system is.\\
\textbf{A.} Adding C++ to a UE4 project shared by a team may cause issues which may make it more difficult to complete this target. If needed, I will remind my teammates on how to avoid these issues. \\
\textbf{R.}  By using my knowledge of C++ and UE4 to create this inventory system, I will gain experience and confidence in my C++ skills.\\
\textbf{T.}  I will complete the first version of the inventory system by the end of the first sprint of the second semester.\\

\section{Conclusion}
Learning to control my frustration and learning how to effectively lead a small team, will help with my long-term goal of taking on a managerial role. Utilising C++ in a complex system,  learning a lightweight app development framework, and being able to have effective breaks will help me to transition into the kind of companies I specified in my career goals.

\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}